The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-04-16 albatros_paper.tex
Add files via upload
Added some text under "Power" subsection.

\subsection{Power}
\textcolor{red}{\bf Tankiso?} \\
Text here about generators.

>>>>

\subsection{Power}

In order to supply power to the whole two-element pathfinder sysytem, a bank of four \SI{12}{V}, \SI{200}{\ampere\hour} batteries were wired in parallel. The Honda EU30is generator is used for charging the battery bank and the fuel is kept in one of the shipping containers at the \prizm\ site. If the batteries are fully charged, the system can fully operate for approximately four days. The power from the battery bank is connected to the Faraday cage where the power regulation is performed. A DC/DC converter stabilises the \SI{12}{V} from the battery bank and further supplies it to the auxiliary regulators that provide step down voltages to various components in the system.
